---
title: "Group_02_Analysis"
author: "Group 02"
format:
  pdf:
    output-file: "Group_01_Analysis"
    output-ext: "pdf"
execute:
  echo: false
  eval: true
  warning: false
  message: false
output:
  pdf_document:
    fig_caption: yes
---

```{r}
library(jsonlite)
library(dplyr)
library(tidyr)
library(sjPlot)
library(janitor)
library(ggplot2)
library(readr)
library(corrplot)
```

# Data

```{r}
Data <- read.csv("dataset02.csv")
Data <- Data %>% select(-Region)#Elements are duplicated
```

# Data Exploration 

```{r}
# Ensure Electricity is treated as a categorical variable
df$Electricity <- as.factor(df$Electricity)

# Select numerical variables.
num_vars <- c("Total.Household.Income", 
              "Total.Food.Expenditure", 
              "Household.Head.Age",
              "Total.Number.of.Family.members", 
              "House.Floor.Area", 
              "House.Age",
              "Number.of.bedrooms")

# Calculate the correlation of numerical variables
cor_matrix <- cor(df[num_vars], use = "complete.obs")
cor_family <- cor_matrix[, "Total.Number.of.Family.members"]

#Select the two most correlated elements
top_2_numeric <- names(sort(abs(cor_family), decreasing = TRUE)[2:3])

# Select categorical variables
cat_vars <- c( "Household.Head.Sex", 
               "Type.of.Household", 
               "Electricity")

# Calculate ANOVA p-value
anova_results <- lapply(cat_vars, function(var) {
  anova_res <- aov(Total.Number.of.Family.members ~ df[[var]], data = df)
  summary(anova_res)[[1]][["Pr(>F)"]][1]  # 提取 p 值
})
anova_results <- unlist(anova_results)
```

We have decided to select the two most correlated numerical variables and the categorical variable with the smallest p-value as our research subjects.

The three selected variables are: **Total.Food.Expenditure, Household.Head.Age, and Type.of.Household.**

```{r}
Data <- Data %>%
  select(Total.Food.Expenditure, Household.Head.Age, Type.of.Household, Total.Number.of.Family.members)
```

# Variable Distribution Visualization

```{r}
# Histogram of Total.Food.Expenditure
ggplot(Data, aes(x = Total.Food.Expenditure)) +
  geom_histogram(aes(y = ..density..), bins = 30, fill = "lightblue", color = "black", alpha = 0.7) +
  geom_density(color = "red", size = 1) +
  labs(title = "Distribution of Total Food Expenditure", x = "Total Food Expenditure", y = "Density")

# Histogram of Household.Head.Age
ggplot(Data, aes(x = Household.Head.Age)) +
  geom_histogram(aes(y = ..density..), bins = 30, fill = "lightgreen", color = "black", alpha = 0.7) +
  geom_density(color = "blue", size = 1) +
  labs(title = "Distribution of Household Head Age", x = "Household Head Age", y = "Density")

# Barchart of Type.of.Household
ggplot(Data, aes(x = Type.of.Household, fill = Type.of.Household)) +
  geom_bar() +
  labs(title = "Count of Household Types", x = "Household Type", y = "Count") +
  theme(legend.position = "none")

# Histogram of Total.Number.of.Family.members
ggplot(Data, aes(x = Total.Number.of.Family.members)) +
  geom_histogram(aes(y = ..density..), bins = 30, fill = "pink", color = "black", alpha = 0.7) +
  geom_density(color = "green", size = 1) +
  labs(title = "Distribution of Total Number of Family members", x = "Total.Number.of.Family.members", y = "Density")
```

# **Data Preprocessing**

```{r}
#Ensure the variable types are correct.
Data$Total.Food.Expenditure <- as.numeric(Data$Total.Food.Expenditure)
Data$Household.Head.Age <- as.numeric(Data$Household.Head.Age)
Data$Total.Number.of.Family.members <- as.numeric(Data$Total.Number.of.Family.members)
Data$Type.of.Household <- as.factor(Data$Type.of.Household)
```

# Modeling with GLM

```{r}
# Perform Poisson regression using GLM modeling.
glm_model <- glm(Total.Number.of.Family.members ~ Total.Food.Expenditure + Household.Head.Age + Type.of.Household, 
                 data = Data, 
                 family = poisson())
summary(glm_model)
```

# GLM Regression Analysis Results

```{r}

```

# **Organize Visualizations (Regression Coefficient Bar Chart, Correlation Heatmap)**

```{r}

```
